Sound Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants

### 2016-10-13 paper/paper.tex
review results

For the majority of our benchmarks, the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, $2$ benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
difference is due to  the fact that the interval back-end does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
a performance difference of at least two orders of magnitude in our experiments, leading to the
interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
lists the faster of the two back-ends for each benchmark, which in $12$ out of $14$ cases is the inductive
back-end.

\begin{table}[H]
\centering
\begin{tabular}{c | l r r | r l}
Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-5}
$G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
$G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
$G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
$G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
$G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
$G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
$G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
$G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
$G_4$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
$G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
$G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
$G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
$G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
$G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
$G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
\end{tabular}

@@

The median runtime for our benchmark set is 318\,s, implying that half of the controllers
can be synthesised in 5 minutes or less using our approach. Overall the average synthesis
time amounts to approximately 30 minutes. With respect to RQ2 we consider
these times short enough to be of practical use to control engineers.
Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks.  For the 1 remaining benchmark our approach failed to synthesise
a stable controller in the requested time limits. This can be addressed by either increasing
the fixed point word widths considered or using floating point arithmetic instead. 
\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
provide link here.}

>>>>

For the majority of our benchmarks, the conjecture explained
in section~\ref{synthesis-elements}  holds and the inductive back-end is able to find a stable
solution in less than one minute.  This is possible if the inductive solutions need to be refined
with few counterexamples and fixed-point precision increases. However, $2$ benchmarks in our set
required too many counterexamples to refine their solution (marked with $^*$ in Table~\ref{tab:results}). 
In these cases, the interval arithmetic back-end is able to complement the inductive approach
and synthesise a solution instead, albeit with significantly larger runtimes.  This performance
difference is due to  the fact that the interval back-end does not take advantage of the inductive
conjecture inherent to CEGIS, but instead fully explores the counterexample space.  The result is
a performance difference of at least two orders of magnitude in our experiments, leading to the
interval back-end timing out on the majority of our benchmarks.  Table~\ref{tab:results} only
lists the faster of the two back-ends for each benchmark, which in $12$ out of $15$ benchmarks is the inductive
back-end.

\begin{table}[H]
\centering
\begin{tabular}{c | c | l | r r | r l}
\# & Plant & Benchmark                  & $I$ & $F$ & Time    & \\\cline{1-6}
1  & $G_1$ & CruiseControl02            &   4 &  16 & 17\,s   & \\
2  & $G_1$ & CruiseControl02$^\dagger$  &   4 &  16 & 46\,s   & \\
3  & $G_2$ & SpringMassDamper           &  15 &  16 & 28\,s   & \\
4  & $G_2$ & SpringMassDamper$^\dagger$ &  15 &  16 & \xmark  & \\
5  & $G_3$ & SatelliteB2                &   3 &   7 & 7\,s    & \\
6  & $G_3$ & SatelliteB2$^\dagger$      &   3 &   7 & 6601\,s & \tbmark\\
7  & $G_3$ & SatelliteC2                &   3 &   5 & 2\,s    & \\
8  & $G_3$ & SatelliteC2$^\dagger$      &   3 &   5 & 76\,s   & \tbmark\\
9  & $G_4$ & a\_ST1\_IMPL1              &  16 &   4 & 2704\,s & \\
10 & $G_4$ & a\_ST1\_IMPL2              &  16 &   8 & 538\,s  & \\
11 & $G_4$ & a\_ST1\_IMPL3              &  16 &  12 & 12\,s   & \\
12 & $G_4$ & a\_ST2\_IMPL1              &  16 &   4 & 318\,s  & \\
13 & $G_4$ & a\_ST2\_IMPL2              &  16 &   8 & 967\,s  & \\
14 & $G_4$ & a\_ST2\_IMPL3              &  16 &  12 & 9798\,s & \\
15 & $G_4$ & a\_ST3\_IMPL1              &  16 &   4 & 6304\,s & \\
\end{tabular}

@@

The median runtime for our benchmark set is $318$\,s, implying that half of the controllers
can be synthesised in $5$ minutes or less using our present approach. Overall the average synthesis
time amounts to approximately $30$ minutes. With respect to RQ2 we consider
these times short enough to be of practical use to control engineers.
Regarding RQ1 we further conclude that the inductive back-end is able to synthesise 
stable controllers in the $12$ out of $15$ benchmarks, and can be complemented using 
the interval arithmetic back-end for $2$ additional benchmarks, where the inductive 
conjectures fail. Both back-ends together enabled controller synthesis for $14$ 
out of $15$ benchmarks.  For the $1$ remaining benchmark our approach failed to synthesise
a stable controller in the requested time limits. This can be addressed by either increasing
the fixed point word widths considered or using floating point arithmetic instead. 
\pksay{TODO: Upload full experiments environment including README and result log files to anonymous Google Drive and
provide link here.}
